---
title: "WI Covid-19 Stats"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



```{r process, echo=FALSE, message=FALSE, warning=FALSE, results = "hide"}
MIN_DATE_INTERVAL <- -3
source("WI_COVID_DATA_PROCESS.R")
Date_lims <- as.Date(c(MAX_DATE %m+% months(MIN_DATE_INTERVAL), MAX_DATE + 1),  "%Y-%m-%d")

```


This document contains confirmed Covid-19 cases, hospitalizations, and deaths in Wisconsin as of `r format(MAX_DATE, format = "%A %B %d, %Y")`.

[See WI DHS for Region Definitions](https://www.dhs.wisconsin.gov/aboutdhs/regions.htm)

# {.tabset}


## State-wide

### Recent

```{r NEW_CASES_STATE, echo=FALSE, warning=FALSE}

PLOT <- ggplot(STATEWIDE_VALUES, aes(Date))
PLOT  + geom_line(aes(y = AVG_7_CHANGE_POS), color = "black") + 
  geom_point(aes(y = CHANGE_POS),color = "red", fill = "red") +  
  geom_point(aes(y = MAX_POS), fill = "blue" ,color = "blue")  + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New Covid-19 Cases", subtitle = "7-day AVG in black, today's value in blue") 

```

&nbsp;

```{r NEW_HOSP_STATE, echo=FALSE, warning=FALSE}

PLOT <- ggplot(STATEWIDE_VALUES, aes(Date))
PLOT  + geom_line(aes(y = AVG_7_CHANGE_HOSP), color = "black") + 
  geom_point(aes(y = CHANGE_HOSP),color = "red", fill = "red") +  
  geom_point(aes(y = MAX_HOSP), fill = "blue" ,color = "blue")  + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New Covid-19 Hospitalizations", subtitle = "7-day AVG in black, today's value in blue") 

```

&nbsp;


```{r NEW_DEATHS_STATE, echo=FALSE, warning=FALSE}

PLOT <- ggplot(STATEWIDE_VALUES, aes(Date))
PLOT  + geom_line(aes(y = AVG_7_CHANGE_DEATHS), color = "black") + 
  geom_point(aes(y = CHANGE_DEATHS),color = "red", fill = "red") +  
  geom_point(aes(y = MAX_DEATHS), fill = "blue" ,color = "blue") + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New Covid-19 Deaths", subtitle =  "7-day AVG in black, today's value in blue") 

```

&nbsp;

* **NEW HOSPITALIZATIONS** are doubling every `r round(Hosp_Doubling, 0)` days (r^2^ = `r round(summary(Hosp_lm)$r.squared, 2)`).

* **NEW DEATHS** are doubling every `r round(Death_Doubling, 0)` days (r^2^ = `r round(summary(Deaths_lm)$r.squared, 2)`).  

Model is fit to mean hospitalizations and deaths for Monday-Thursday and Friday-Sunday periods to reduce variability due to day of the week.


```{r NEW_DEATHS_STATE_LOG, echo=FALSE, warning=FALSE}

PLOT <- ggplot(STATEWIDE_VALUES_SMOOTH, aes(x = Date))
PLOT  + geom_point(aes(y = mean_CHANGE_DEATHS), color = "red", fill = "red") +  
  stat_smooth(aes(y = mean_CHANGE_DEATHS), method = "lm",formula = y~x,  col = "red") +
 geom_point(aes(y = mean_CHANGE_HOSP), color = "blue", fill = "blue") +  
  stat_smooth(aes(y = mean_CHANGE_HOSP), method = "lm",formula = y~x, col = "blue") +
  scale_y_log10()+
  scale_x_date(limits = date(c(lm_DATE_MIN, MAX_DATE))) +
  labs(y = "New Hosp./Deaths", title  = "Exponential Growth in New Hospitalizations and Deaths", subtitle =  "Hosp. in blue, deaths in red, line slope represents exponential growth rate") 

```





<!-- ```{r NEW_CASES_HOSP_DEATH, echo=FALSE, warning=FALSE} -->

<!-- PLOT <- ggplot(STATEWIDE_VALUES, aes(Date)) -->
<!-- PLOT  + geom_line(aes(y = AVG_7_CHANGE_DEATHS_percent), color = "red") +  -->
<!--   geom_line(aes(y = AVG_7_CHANGE_HOSP_percent), color = "blue") + -->
<!--   geom_line(aes(y = AVG_7_CHANGE_POS_percent), color = "black") +  -->
<!--   scale_x_date(limits = Date_lims) + -->
<!--   labs(y = "", title  = "7-day AVG of Cases, Hosp., and Deaths")  -->

<!-- ``` -->






### Since Beginning of Pandemic

```{r NEW_CASES_STATE_ALL, echo=FALSE, warning=FALSE}

PLOT <- ggplot(STATEWIDE_VALUES, aes(Date))
PLOT  + geom_line(aes(y = AVG_7_CHANGE_POS), color = "black") + 
  geom_point(aes(y = CHANGE_POS),color = "red", fill = "red") +  
  geom_point(aes(y = MAX_POS), fill = "blue" ,color = "blue") + 
  #scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New Covid-19 Cases", subtitle =  "7-day AVG in black, today's value in blue") 

```

&nbsp;


```{r NEW_HOSP_STATE_ALL, echo=FALSE, warning=FALSE}

PLOT <- ggplot(STATEWIDE_VALUES, aes(Date))
PLOT  + geom_line(aes(y = AVG_7_CHANGE_HOSP), color = "black") + 
  geom_point(aes(y = CHANGE_HOSP),color = "red", fill = "red") +  
  geom_point(aes(y = MAX_HOSP), fill = "blue" ,color = "blue")  + 
  #scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New Covid-19 Hospitalizations" , subtitle =  "7-day AVG in black, today's value in blue") 

```

&nbsp;



```{r NEW_DEATHS_STATE_ALL, echo=FALSE, warning=FALSE}

PLOT <- ggplot(STATEWIDE_VALUES, aes(Date))
PLOT  + geom_line(aes(y = AVG_7_CHANGE_DEATHS), color = "black") + 
  geom_point(aes(y = CHANGE_DEATHS),color = "red", fill = "red") +  
  geom_point(aes(y = MAX_DEATHS), fill = "blue" ,color = "blue") + 
  #scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New Covid-19 Deaths", subtitle =  "7-day AVG in black, today's value in blue") 

```





## Regions 

```{r NEW_AVG_REGION, echo=FALSE, warning=FALSE}

PLOT <- ggplot(REGION_VALUES, aes(x = Date, y = AVG_7_CHANGE_POS))
PLOT + geom_line(aes(color = REGION, group = REGION)) + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New Covid-19 Cases (7-day trailing average)") 
```


&nbsp;

```{r NEW_TOTAL_REGION, echo=FALSE, warning=FALSE}

PLOT <- ggplot(REGION_VALUES, aes(fill = REGION, x = Date, y = CHANGE_POS))
PLOT + geom_bar(position = "stack", stat = "identity") + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New Covid-19 Cases") 
```

&nbsp;

```{r REGION_PERCENT, echo=FALSE, warning=FALSE}
PLOT <- ggplot(REGION_VALUES, aes(Date, AVG_7_PERCENT_POS))
PLOT + geom_line(aes(color = REGION, group = REGION)) + 
    scale_x_date(limits = Date_lims) +
  labs(y = "", title = "Prop. Positive Tests (7-day trailing average)") + ylim(0,.45)

```


&nbsp;




```{r NEW_AVG_HOSP_REGION, echo=FALSE, warning=FALSE}

PLOT <- ggplot(REGION_VALUES, aes(x = Date, y = AVG_7_CHANGE_HOSP))
PLOT + geom_line(aes(color = REGION, group = REGION)) + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New Covid-19 Hospitalizations (7-day trailing average)") 
```

&nbsp;


```{r NEW_AVG_DEATHS_REGION, echo=FALSE, warning=FALSE}

PLOT <- ggplot(REGION_VALUES, aes(x = Date, y = AVG_7_CHANGE_DEATHS))
PLOT + geom_line(aes(color = REGION, group = REGION)) + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New Covid-19 Deaths (7-day trailing average)") 
```

&nbsp;



```{r REGION_TOTAL, echo=FALSE, warning=FALSE}
#require(scales)
PLOT <- ggplot(REGION_VALUES, aes(Date, POSITIVE))
PLOT + geom_line(aes(color = REGION, group = REGION)) +
  scale_y_log10(labels = scales::comma) + labs(y = "", title  = "Total Covid-19 Cases (Log Scale)")
```


&nbsp;


```{r REGION_PER, echo=FALSE, warning=FALSE}
PLOT <- ggplot(REGION_VALUES, aes(Date, REGION_POSITIVE_PER_THOUS))

PLOT + geom_line(aes(color = REGION, group = REGION)) +  labs(y = "", title = "Total Covid-19 Cases per 1000 People")
```










## Most Populous Counties


```{r NEW_AVG_COUNTY, echo=FALSE, warning=FALSE}

PLOT <- ggplot(COUNTY_VALUES_TOP_6_COUNTIES, aes(x = Date, y = AVG_7_CHANGE_POS))
PLOT + geom_line(aes(color = COUNTY, group = COUNTY)) + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```


<!-- &nbsp; -->


<!-- ```{r Largest_Counties_PERCENT, echo=FALSE, warning=FALSE} -->
<!-- PLOT <- ggplot(COUNTY_VALUES_TOP_6_COUNTIES, aes(Date, AVG_7_PERCENT_POS)) -->
<!-- PLOT + geom_line(aes(color = COUNTY, group = COUNTY)) +  -->
<!--   scale_x_date(limits = Date_lims) + -->
<!--   labs(y = "", title = "Prop. Positive Tests (7-day trailing average)") + ylim(0,.45) -->

<!-- ``` -->




&nbsp;



```{r Largest_Counties_TOTAL, echo=FALSE, warning=FALSE}


PLOT <- ggplot(COUNTY_VALUES_TOP_6_COUNTIES, aes(Date, POSITIVE))
PLOT + geom_line(aes(color = COUNTY, group = COUNTY)) + scale_y_log10() + labs(y = "", title  = "Total Covid-19 Cases (Log Scale)")
```


&nbsp;


```{r Largest_Counties_PER, echo=FALSE, warning=FALSE}
PLOT <- ggplot(COUNTY_VALUES_TOP_6_COUNTIES, aes(Date, COUNTY_POSITIVE_PER_THOUS))
PLOT + geom_line(aes(color = COUNTY, group = COUNTY)) +  labs(y = "", title = "Total Covid-19 Cases per 1000 People")
```



## Select Counties

```{r NEW_TOTAL_SELECT, echo=FALSE, warning=FALSE}

PLOT <- ggplot(COUNTY_VALUES_SELECT, aes(Date))
PLOT  + geom_line(aes(y = AVG_7_CHANGE_POS), color = "black") + geom_point(aes(y = CHANGE_POS), fill = "red" ,color = "red") + geom_point(aes(y = MAX_POS), fill = "blue" ,color = "blue") + 
  scale_x_date(limits = Date_lims) +
  facet_wrap(~ COUNTY, ncol = 2, scales = "free")   +  labs(y = "", title  = "New Covid-19 Cases (7-day AVG in black, today's value in blue)") 

```

## Most Pop. Counties by Region

### North

```{r NEW_AVG_COUNTY_NORTH, echo=FALSE, warning=FALSE}

PLOT <- ggplot(COUNTY_VALUES_TOP_6_EACH_REGION[which(COUNTY_VALUES_TOP_6_EACH_REGION$REGION == "N"),], aes(x = Date, y = AVG_7_CHANGE_POS))
PLOT + geom_line(aes(color = COUNTY, group = COUNTY)) + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```


### Northeast

```{r NEW_AVG_COUNTY_NORTHEAST, echo=FALSE, warning=FALSE}

PLOT <- ggplot(COUNTY_VALUES_TOP_6_EACH_REGION[which(COUNTY_VALUES_TOP_6_EACH_REGION$REGION == "NE"),], aes(x = Date, y = AVG_7_CHANGE_POS))
PLOT + geom_line(aes(color = COUNTY, group = COUNTY)) + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```


### South

```{r NEW_AVG_COUNTY_SOUTH, echo=FALSE, warning=FALSE}

PLOT <- ggplot(COUNTY_VALUES_TOP_6_EACH_REGION[which(COUNTY_VALUES_TOP_6_EACH_REGION$REGION == "S"),], aes(x = Date, y = AVG_7_CHANGE_POS))
PLOT + geom_line(aes(color = COUNTY, group = COUNTY)) + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```

### Southeast


```{r NEW_AVG_COUNTY_SOUTHEAST, echo=FALSE, warning=FALSE}

PLOT <- ggplot(COUNTY_VALUES_TOP_6_EACH_REGION[which(COUNTY_VALUES_TOP_6_EACH_REGION$REGION == "SE"),], aes(x = Date, y = AVG_7_CHANGE_POS))
PLOT + geom_line(aes(color = COUNTY, group = COUNTY)) + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```

### West

```{r NEW_AVG_COUNTY_WEST, echo=FALSE, warning=FALSE}

PLOT <- ggplot(COUNTY_VALUES_TOP_6_EACH_REGION[which(COUNTY_VALUES_TOP_6_EACH_REGION$REGION == "W"),], aes(x = Date, y = AVG_7_CHANGE_POS))
PLOT + geom_line(aes(color = COUNTY, group = COUNTY)) + 
  scale_x_date(limits = Date_lims) +
  labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```



# {-}
By Michael J Zenz
&nbsp;
mail (at) mjzenz (dot) org
&nbsp;
[mjzenz.org](https://www.mjzenz.org)
&nbsp;
[github](https://github.com/mjzenz/WI-Covid)
&nbsp;
`r Sys.time()`


