---
title: "WI Covid-19 Stats (past 3 months)"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



```{r process, echo=FALSE, message=FALSE, warning=FALSE, results = "hide"}
source("WI_COVID_DATA_PROCESS.R")
```


This document contains confirmed Covid-19 cases, hospitalizations, and deaths for the past 3 months as of `r format(MAX_DATE, format = "%A %B %d, %Y")`.

# {.tabset}

## Regions 
[See WI DHS for Region Definitions](https://www.dhs.wisconsin.gov/aboutdhs/regions.htm)

```{r NEW_AVG_REGION, echo=FALSE, warning=FALSE}

REGION_AVG_VALUES_POSITIVE <- ggplot(REGION_VALUES, aes(x = Date, y = AVG_7_CHANGE_POS))
REGION_AVG_VALUES_POSITIVE + geom_line(aes(color = REGION, group = REGION)) + labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)") 
```


&nbsp;

```{r NEW_TOTAL_REGION, echo=FALSE, warning=FALSE}

REGION_NEW_VALUES_POSITIVE <- ggplot(REGION_VALUES, aes(fill = REGION, x = Date, y = CHANGE_POS))
REGION_NEW_VALUES_POSITIVE + geom_bar(position = "stack", stat = "identity") + labs(y = "", title  = "New Daily Covid-19 Cases") 
```


&nbsp;



```{r REGION_TOTAL, echo=FALSE, warning=FALSE}


REGION_VALUES_POSITIVE <- ggplot(REGION_VALUES, aes(Date, POSITIVE))
REGION_VALUES_POSITIVE + geom_line(aes(color = REGION, group = REGION)) + scale_y_log10() + labs(y = "", title  = "Total Covid-19 Cases (Log Scale)")
```


&nbsp;


```{r REGION_PER, echo=FALSE, warning=FALSE}
REGION_POSITIVE_PER_THOUS <- ggplot(REGION_VALUES, aes(Date, REGION_POSITIVE_PER_THOUS))

REGION_POSITIVE_PER_THOUS + geom_line(aes(color = REGION, group = REGION)) +  labs(y = "", title = "Total Covid-19 Cases per 1000 People")
```



&nbsp;


```{r REGION_PERCENT, echo=FALSE, warning=FALSE}
REGION_PERCENT_POSITIVE <- ggplot(REGION_VALUES, aes(Date, AVG_7_PERCENT_POS))
REGION_PERCENT_POSITIVE + geom_line(aes(color = REGION, group = REGION)) + labs(y = "", title = "Prop. Positive Tests (7-day trailing average)") + ylim(0,.45)

```



&nbsp;



## Most Populous Counties


```{r NEW_AVG_COUNTY, echo=FALSE, warning=FALSE}

COUNTY_AVG_VALUES_POSITIVE <- ggplot(COUNTY_VALUES_TOP_6_COUNTIES, aes(x = Date, y = AVG_7_CHANGE_POS))
COUNTY_AVG_VALUES_POSITIVE + geom_line(aes(color = COUNTY, group = COUNTY)) + labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```




```{r Largest_Counties_TOTAL, echo=FALSE, warning=FALSE}


TOP_6_COUNTIES_POSITIVE <- ggplot(COUNTY_VALUES_TOP_6_COUNTIES, aes(Date, POSITIVE))
TOP_6_COUNTIES_POSITIVE + geom_line(aes(color = COUNTY, group = COUNTY)) + scale_y_log10() + labs(y = "", title  = "Total Covid-19 Cases (Log Scale)")
```


&nbsp;


```{r Largest_Counties_PER, echo=FALSE, warning=FALSE}
TOP_6_COUNTIES_POSITIVE_PER_THOUS <- ggplot(COUNTY_VALUES_TOP_6_COUNTIES, aes(Date, COUNTY_POSITIVE_PER_THOUS))

TOP_6_COUNTIES_POSITIVE_PER_THOUS + geom_line(aes(color = COUNTY, group = COUNTY)) +  labs(y = "", title = "Total Covid-19 Cases per 1000 People")
```

&nbsp;


```{r Largest_Counties_PERCENT, echo=FALSE, warning=FALSE}
TOP_6_COUNTIES_PERCENT_POSITIVE <- ggplot(COUNTY_VALUES_TOP_6_COUNTIES, aes(Date, AVG_7_PERCENT_POS))
TOP_6_COUNTIES_PERCENT_POSITIVE + geom_line(aes(color = COUNTY, group = COUNTY)) + labs(y = "", title = "Prop. Positive Tests (7-day trailing average)") + ylim(0,.45)

```


## New Positive Cases in Select Counties

```{r NEW_TOTAL_SELECT, echo=FALSE, warning=FALSE}

SELECT_COUNTY_NEW_VALUES_POSITIVE <- ggplot(COUNTY_VALUES_SELECT, aes(Date))
SELECT_COUNTY_NEW_VALUES_POSITIVE  + geom_line(aes(y = AVG_7_CHANGE_POS), color = "black") + geom_point(aes(y = CHANGE_POS), fill = "red" ,color = "red") + geom_point(aes(y = MAX_POS), fill = "blue" ,color = "blue") + facet_wrap(~ COUNTY, ncol = 2, scales = "free")   +  labs(y = "", title  = "Daily CTY Cases (7-day AVG in black, today's value in blue)") 

```

## Avg. New Pos. Cases in Most Pop. Counties by Region

### North

```{r NEW_AVG_COUNTY_NORTH, echo=FALSE, warning=FALSE}

COUNTY_AVG_VALUES_POSITIVE_NORTH <- ggplot(COUNTY_VALUES_TOP_6_EACH_REGION[which(COUNTY_VALUES_TOP_6_EACH_REGION$REGION == "N"),], aes(x = Date, y = AVG_7_CHANGE_POS))
COUNTY_AVG_VALUES_POSITIVE_NORTH + geom_line(aes(color = COUNTY, group = COUNTY)) + labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```


### Northeast

```{r NEW_AVG_COUNTY_NORTHEAST, echo=FALSE, warning=FALSE}

COUNTY_AVG_VALUES_POSITIVE_NORTHEAST <- ggplot(COUNTY_VALUES_TOP_6_EACH_REGION[which(COUNTY_VALUES_TOP_6_EACH_REGION$REGION == "NE"),], aes(x = Date, y = AVG_7_CHANGE_POS))
COUNTY_AVG_VALUES_POSITIVE_NORTHEAST + geom_line(aes(color = COUNTY, group = COUNTY)) + labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```


### South

```{r NEW_AVG_COUNTY_SOUTH, echo=FALSE, warning=FALSE}

COUNTY_AVG_VALUES_POSITIVE_SOUTH <- ggplot(COUNTY_VALUES_TOP_6_EACH_REGION[which(COUNTY_VALUES_TOP_6_EACH_REGION$REGION == "S"),], aes(x = Date, y = AVG_7_CHANGE_POS))
COUNTY_AVG_VALUES_POSITIVE_SOUTH + geom_line(aes(color = COUNTY, group = COUNTY)) + labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```

### Southeast


```{r NEW_AVG_COUNTY_SOUTHEAST, echo=FALSE, warning=FALSE}

COUNTY_AVG_VALUES_POSITIVE_SOUTHEAST <- ggplot(COUNTY_VALUES_TOP_6_EACH_REGION[which(COUNTY_VALUES_TOP_6_EACH_REGION$REGION == "SE"),], aes(x = Date, y = AVG_7_CHANGE_POS))
COUNTY_AVG_VALUES_POSITIVE_SOUTHEAST + geom_line(aes(color = COUNTY, group = COUNTY)) + labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```

### West

```{r NEW_AVG_COUNTY_WEST, echo=FALSE, warning=FALSE}

COUNTY_AVG_VALUES_POSITIVE_WEST <- ggplot(COUNTY_VALUES_TOP_6_EACH_REGION[which(COUNTY_VALUES_TOP_6_EACH_REGION$REGION == "W"),], aes(x = Date, y = AVG_7_CHANGE_POS))
COUNTY_AVG_VALUES_POSITIVE_WEST + geom_line(aes(color = COUNTY, group = COUNTY)) + labs(y = "", title  = "New  Covid-19 Cases (7-day trailing average)")
```

## New Hospitalizations


```{r NEW_HOSP_STATE, echo=FALSE, warning=FALSE}

STATEWIDE_NEW_DEATHS <- ggplot(STATEWIDE_VALUES, aes(Date))
STATEWIDE_NEW_DEATHS  + geom_line(aes(y = AVG_7_CHANGE_HOSP), color = "black") + geom_point(aes(y = CHANGE_HOSP),color = "red", fill = "red") +  geom_point(aes(y = MAX_HOSP), fill = "blue" ,color = "blue") + labs(y = "", title  = "New WI Covid-19 Hospitalizations (7-day AVG in black, today's value in blue)") 

```




```{r NEW_AVG_HOSP_REGION, echo=FALSE, warning=FALSE}

REGION_AVG_HOSP_VALUES_POSITIVE <- ggplot(REGION_VALUES, aes(x = Date, y = AVG_7_CHANGE_HOSP))
REGION_AVG_HOSP_VALUES_POSITIVE + geom_line(aes(color = REGION, group = REGION)) + labs(y = "", title  = "New Covid-19 Hospitalizations (7-day trailing average)") 
```

## New Deaths

```{r NEW_DEATHS_STATE, echo=FALSE, warning=FALSE}

STATEWIDE_NEW_DEATHS <- ggplot(STATEWIDE_VALUES, aes(Date))
STATEWIDE_NEW_DEATHS  + geom_line(aes(y = AVG_7_CHANGE_DEATHS), color = "black") + geom_point(aes(y = CHANGE_DEATHS),color = "red", fill = "red") +  geom_point(aes(y = MAX_DEATHS), fill = "blue" ,color = "blue") + labs(y = "", title  = "Daily WI Covid-19 Deaths (7-day AVG in black, today's value in blue)") 

```







# {-}
By Michael J Zenz
&nbsp;
mail (at) mjzenz (dot) org
&nbsp;
[mjzenz.org](https://www.mjzenz.org)
&nbsp;
[github](https://github.com/mjzenz/WI-Covid)
&nbsp;
`r Sys.time()`


